dispRity manual

### 2018-03-19 inst/gitbook/02_getting-started.Rmd
Matt's suggestion for gitbook

## Performing a simple dispRity analysis

@@

## Testing for a difference between the groups
test.dispRity(disparity_data, test = wilcox.test, details = TRUE)
```

>>>>

## Performing a simple dispRity analysis {#simpleanalysis}

@@

## Testing for a difference between the groups
test.dispRity(disparity_data, test = wilcox.test, details = TRUE)
```
<!-- 
## Minimalist example

This is the minimal and simplest analysis you can perform in `dispRity`, regardless of the question, data, metric and test.
I strongly suggest to read [Simple Analysis section](#simpleanalysis) or the [specific tutorials](#specific-tutorial) for more info.

 1. Collect data prior to using the `dispRity` package

```{r}
## Generating a random space by combining two matrices
## from two different random normal distributions
distribution1 <- matrix(rnorm(25, mean = 1), 5, 5, dimnames = list(letters[1:5] ))
distribution2 <- matrix(rnorm(25, mean = 5), 5, 5, dimnames = list(letters[6:10]))
random_space <- rbind(distribution1, distribution2)
```

 2. Load the package

```{r}
library(dispRity)
```

 3. Create two subsets (the two different distributions)

```{r}
## Creating different subsets for each distribution
(two_subsets <- custom.subsets(random_space, group = list(letters[1:5], letters[6:10])))
```

 4. Bootstrap the subsets

```{r}
## Bootstrap the data
(bootstrapped_subsets <- boot.matrix(two_subsets))
```

 5. Calculate disparity as the median distance from each group's element to their centroid

```{r}
## Calculate disparity
(disparity <- dispRity(bootstrapped_subsets, metric = c(median, centroids)))
```

 6. Summarising the results

```{r, fig.width=7, fig.height=7}
## Summarising the results
summary(disparity)

## Plotting them
plot(disparity)
```

 7. Testing whether the groups are different

```{r}
## Testing if the mean bootstrap values are different between groups
test.dispRity(disparity, test = t.test)
``` -->

### 2018-03-19 inst/gitbook/index.Rmd
changed summary to proper S3 method
Updated book
Matt's suggestion for gitbook

This is a package for measuring disparity in `R`.
It allows users to summarise matrices as representations as multidimensional spaces into a single value or distribution describing a specific aspect of this multidimensional space (the disparity).
Multidimensional spaces can be ordinated matrices from MDS, PCA, PCO, PCoA but the package is *not* restricted to any type of matrices!
This manual is based on the version `0.5.0`.

@@

Note that this citation is only temporary (but can still be used!).
A proper description of the package is currently in review in Methods in Ecology and Evolution and should be re-submitted this winter.
Upon acceptance (hopefully!), a proper DOI will be released for this manual and the package description.

>>>>

This is a package for measuring disparity in `R`.
It allows users to summarise matrices as representations as multidimensional spaces into a single value or distribution describing a specific aspect of this multidimensional space (the disparity).
Multidimensional spaces can be ordinated matrices from MDS, PCA, PCO, PCoA but the package is *not* restricted to any type of matrices!
This manual is based on the version `1.0.0`.

@@

Note that this citation is only temporary (but can still be used!).
A proper description of the package is currently in review in Methods in Ecology and Evolution.
Upon acceptance (hopefully!), a proper DOI will be released for this manual and the package description.
